%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Lead Embedded Systems Software Engineer \& Web Administrator} % Job title
{Summit Technology} % Organization
{Pleasant Hill, CA} % Location
{Mar. 2017 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed the defining feature of the company's latest enterprise-level power analyzer; I oversaw each aspect of the software development life-cycle (SDLC) from planning and analysis, architectural design, software development, testing and deployment, to maintenance, in conjunction with the CEO, sales and marketing team, hardware team, and software team.}
\item {Built a fundamental graphical user interface (GUI) with its own API, spanning 30 files and 28,000 lines of C code on the ARM processor, using the STemWin Embedded Graphics Library for the power analyzer's LCD display -- the aforementioned defining feature.}
\item {Analysis and processing of voltage, current, power, harmonic, and other related data to create real-time graphs and tables for detailed power analysis.}
\item {Created a remote control system that can send screen data and receive commands under strict space and time constraints using custom designed data packets in conjunction with the software team.}
\item {Comprehensive usage of the I-Jet Trace debugger to determine actual run-time and ensure that code meets strict time and space constraints on the embedded target}
\item {Managed website security by maintaining and implementing HTTPS \& SSL security, firewalls, and malware scanners; discovered and removed web injection malware, prevented denial of service attacks.}
\item {Managed website infrastructure including web server, web host, domain host, mail servers, file transfer protocol (FTP), and user access.
\item {Created and maintained web content, implemented e-commerce shopping cart and products; kept website up to date, backed-up, and optimized for speed and web searches (SEO).}}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Web Developer} % Job title
{Summit Technology} % Organization
{Pleasant Hill, CA} % Location
{Jun. 2016 - Feb. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Built and maintained the company website, which is still in use to this day.}
\item {Made thoroughly researched executive decisions, such as using the WordPress Framework so that the website could be easily added to, edited, and maintained by the sales and marketing team.}
\item {Developed a limited in-house HTML/CSS API such that a layperson could easily create specialized design content such as sliders, menus, and product pages.}
\item {Built a custom quote request form with complex conditional logic, validation, data sanitization, informative tool-tips and dialogues, submission logging, and SMTP email generation with attached PDF invoices and estimates using the jQuery UI API and PHP DomPDF API.}
\item {Comprehensive documentation of the API and custom form for future use and development.}
\item {Website speed and search engine optimization (SEO) using a wide variety of audit tools such as Google Analytics, Google PageSpeed, Google Lighthouse, GTMetrix, and WPRocket.}
\end{cvitems}
}

%------------------------------------------------


\end{cventries}